---
title: "Homework 4"
output: html_notebook
---

| Homework 4                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Sep 20  | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 4. Refer to the corresponding materials and
ICE (with solutions) posted on ICON.

Follow all of the guidelines given on prior homeworks, referring to
them as necessary. Here are some important reminders:

- include the required `library(...)` commands in your notebook;

- for this assignment, be sure to use `qplot(...)` instead of `plot(...)`.

- while we used `log` in our module examples, in general only use `log`
when you have a good reason to do so (e.g., correcting the shape of a
histogram); I will indicate when to do this.

**Big Hint!** The exercises below ask you to save your outputs to PNGs
files. In general, get into the habit of first exporting your graphic
with `ggsave(...)` *before* checking to see if the graphic looks correct.
The plot within an R notebook will look different than the final output
file, and yet the output file should be considered the final version
(since, for example, it could be added to a report). Your homework will
be graded by regenerating the graphics files from your notebook. There
is no need to upload your output files to GitHub.

# Exercises

```{r}
# Load some libraries. You may need additional ones
library(readr)
library(forcats)
suppressPackageStartupMessages(library(dplyr))

```

Carefully review the included files `movies.txt` and
`movies_transformed.csv` and then execute the following code to load the
CSV file, which matches the solution of the previous homework. Then
complete the exercises below:

```{r}
my_col_types <- cols(
    OpeningDate = col_date(),
    Title = col_character(),
    Studio = readr::col_factor(), # "readr::" prefix avoids conflict with scales
    OpeningGross = col_integer(),
    OpeningTheaters = col_integer(),
    TotalGross = col_integer(),
    TotalTheaters = col_integer(),
    GrossRatio = col_double(),
    Stamina = readr::col_factor() # "readr::" prefix avoids conflict with scales
)
df <- read_csv("movies_transformed.csv", col_types = my_col_types)
new_levels <- levels(df$Studio)
new_levels <- setdiff(new_levels, "Other")
new_levels <- sort(new_levels)
new_levels <- c(new_levels, "Other")
df <- mutate(df, Studio = fct_relevel(Studio, new_levels))
```

## #1

Complete the following *without* changing the contents of `df`.

### (a)

Create a graphic based on a single integer/numeric/double column
of data. (Do not use two or more columns to build this graphic.) You
can choose the column and the type of graphic. Export the graphic to
a PNG file named `1a.png` via the `ggsave(...)` command with option
`dpi=600`.

```{r}

```

### (b)

Create a graphic based on a single factor column of data. (Do
not use two or more columns to build this graphic.) You can choose the
column and the type of graphic. Export the graphic to a PNG file named
`1b.png` via the `ggsave(...)` command with option `dpi=600`.

```{r}

```

### (c)

Create a scatter plot based on exactly two
integer/numeric/double columns of data. (Do not use three or more
columns to build this graphic.) You can choose the columns. Export the
graphic to a PNG file named `1c.png` via the `ggsave(...)` command with
option `dpi=600`.

```{r}

```

### (d)

Create a heatmap based on exactly two integer/numeric/double
columns of data. (Do not use three or more columns to build this
graphic.) You can choose the columns. Export the graphic to a PNG file
named `1d.png` via the `ggsave(...)` command with option `dpi=600`.

```{r}

```

### (e)

Create boxplots of an integer/numeric/double column on a log
scale against a factor column. You can choose the columns. Export the
graphic to a PNG file named `1e.png` via the `ggsave(...)` command with
option `dpi=600`.

```{r}

```

### (f)

Use faceting to create a graphic involving exactly two factor
columns. (Do not use three or more columns to build this graphic.)
Export the graphic to a PNG file named `1f.png` via the `ggsave(...)`
command with option `dpi=600`.

```{r}

```

## #2

Without changing the contents of df, create a graphic involving three
or more columns of data. You can choose all features of the graphic, but
please adhere to the following rules:

- Produce the graphic with the following audience in mind: a colleague,
friend, or family member who is familiar with movies and who has
experience reading and understanding graphics of various types, e.g.,
boxplots in a trade magazine. (Your classmates or the professor---people
who are looking at the data to the same level of detail---are *not* the
target audience.)

- Give the graphic a main title, which helps explain the graphic. Here
are some example titles: "Number of Movies Per Studio" and "Gross Ticket
Sales Versus Number of Theaters".

- Relabel axis titles and legend titles so that they are readable and
understandable.

- Relabel the numbers on axes so that they are readable and
understandable, e.g., avoid scientific notation and use "$" for dollar
amounts.

- Make sure no text is accidentally cut out of the graphic. Also make
sure text does not overlap.

- Export the graphic to a PNG file named `2.png` via the `ggsave(...)`
command with option `dpi=600`. Also use options `width=6` and `height=4`
unless you have a good reason to deviate from these defaults. (Making
the graphic easier to read and understand is a good reason to deviate.)

```{r}

```
